Accounting for uncertainty in simulation greenhouse gas emissions from dairy cattle in Kenya

### 2022-05-15 Manuscript_analyses.Rmd
added scenarios

---
title: "Manuscript_analyses"
author: "Eike Luedeling, Cory Whitney, Todd Rosenstock"
date: "5/12/2022"
output: html_document
---

# Accounting for uncertainty in simulation greenhouse gas emissions from dairy cattle in Kenya

## Set up

@@

## Monte Carlo simulation

@@

## Running a Monte Carlo simulation with scenarios

@@

## Household-based scenarios

@@

## Possible errors resulting from input uncertainty

@@

ggplot(data=farm5_emissions$y, aes(CO2eq_per_milk)) +
geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") +
  ylab("Relative probability") +
    xlab(expression(Emission~density~of~milk~production~(XX~CO[2]-eq~kg^-1)))

@@

# UNIT NEEDS TO BE ADDED HERE (and checked for milk, though this is probably right)
# ALSO need to add the usual precise value estimate

@@

## Milk_yield (x-axis) effect on on-farm GHG emissions (y-axis)

@@

GHG_simulation_scenarios$y<-GHG_simulation_scenarios$y[which(GHG_simulation_scenarios$y$pc_milk_yield>500),]

#GHG_simulation_scenarios$y<-GHG_simulation_scenarios$y[is.finite(GHG_simulation_scenarios$y$CO2eq_per_milk),]

#GHG_simulation_scenarios$y[GHG_simulation_scenarios$y[,"CO2eq_per_milk"]>10,]

#GHG_simulation_scenarios$y
```

@@

uncertainty::varscatter(in_var = GHG_simulation_scenarios$y$pc_milk_yield,
                        out_var = GHG_simulation_scenarios$y$CO2eq_per_milk,
                        xlab = expression(Total~milk~yield~(kg~head^{-1}~year^{-1})),
                        ylab = expression(Total~emissions~intensity~of~milk~production~(kg~CO[2]-eq~kg^{-1})))
```

@@

```{r varkernel}
uncertainty::varkernel(in_var = GHG_simulation_scenarios$y$pc_milk_yield,
                        out_var = GHG_simulation_scenarios$y$CO2eq_per_milk,
                        xlab = expression(Total~milk~yield~(kg~head^{-1}~year^{-1})),
                        ylab = expression(Total~emissions~intensity~of~milk~production~(kg~CO[2]-eq~kg^{-1})))
```

# THIS LOOKS BAD, BECAUSE OF Low-Milk-high-emissions households. Would be good to break the axis - any ideas?

@@

## Probability of GHG emissions for a given range of milk yield

```{r varkernelslicerange}
slice<-uncertainty::varslice_resample(in_var = GHG_simulation_scenarios$y$pc_milk_yield,
                                 out_var = GHG_simulation_scenarios$y$CO2eq_per_milk, 
                                 expectedin_var=2000,
                           n = 1000,
                           n_samples = 1000,
                           out_var_sampling = (max(out_var)-min(out_var))/1000)

@@

@@

# THIS WON'T REALLY WORK... peak is too high, everything else becomes invisible

>>>>

---
title: "Accounting for uncertainty in simulation greenhouse gas emissions from dairy cattle in Kenya"
author: "Eike Luedeling, Cory Whitney, Todd Rosenstock"
date: "5/12/2022"
output: html_document
---

# Set up

@@

# Monte Carlo simulation

@@

# Running a Monte Carlo simulation with scenarios

@@

# Household-based scenarios

@@

# Possible errors resulting from input uncertainty

@@

ggplot(data=farm5_emissions$y, aes(CO2eq_per_milk)) +
geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") +
  ylab("Relative probability") +
    xlab(expression(Emission~density~of~milk~production~(kg~CO[2]-eq~kg^-1)))

@@

# STILL NEED TO add the usual precise value estimate

@@

# Emissions intensity of milk production

@@

normal_milk_yield<-which(GHG_simulation_scenarios$y$pc_milk_yield>500)

dairy_households<-GHG_simulation_scenarios
dairy_households$x<-dairy_households$x[normal_milk_yield,]
dairy_households$y<-dairy_households$y[normal_milk_yield,]

@@

uncertainty::varscatter(in_var = dairy_households$y$pc_milk_yield,
                        out_var = dairy_households$y$CO2eq_per_milk,
                        xlab = expression(Total~milk~yield~(kg~head^{-1}~year^{-1})),
                        ylab = expression(Total~emissions~intensity~of~milk~production~(kg~CO[2]-eq~kg^{-1})))
```

@@

```{r varkernel}
uncertainty::varkernel(in_var = dairy_households$y$pc_milk_yield,
                        out_var = dairy_households$y$CO2eq_per_milk,
                        xlab = expression(Total~milk~yield~(kg~head^{-1}~year^{-1})),
                        ylab = expression(Total~emissions~intensity~of~milk~production~(kg~CO[2]-eq~kg^{-1})))
```

@@

# Probability of GHG emissions for a given milk yield

The following plot shows the emissions intensity that corresponds to a milk yield of 2000 kg per capita per year, based on the population of households covered in the survey.

```{r varkernelslicerange}
slice<-uncertainty::varslice_resample(in_var = dairy_households$y$pc_milk_yield,
                                 out_var = dairy_households$y$CO2eq_per_milk, 
                                 expectedin_var=2000,
                           n = 1000,
                           n_samples = 1000,
                           out_var_sampling = 1000)

@@

ggplot(data=data.frame(CO2eq_per_milk=slice$resampled), aes(CO2eq_per_milk)) +
geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") +
  ylab("Relative probability") +
    xlab(expression(Emission~density~of~milk~production~at~2000~kg~milk~per~capita~(XX~CO[2]-eq~kg^-1)))

ggsave("Fig_X_emission_density_all_farms.png")

@@

We see considerable uncertainty about the emissions at this particular level of production, and the previous figure shows that emissions of all other levels is similarly variable. This raises considerable doubts about the usefulness of milk yield as an indicator of emissions intensity - at least when this indicator is taken at face value, without considering this uncertainty. Yet, some information is contained even in such an imperfect indicator, since, as also shown in the previous figure, there is clearly a correlation between milk yield and emissions intensity. The following proposes a mechanism for quantifying the level of certainty, with which a change in milk yield can reasonably be associated with a change in emissions intensity.

# Probability of an increase in milk yield being associated with an increase in GHG emission intensity

To derive the level of certainty, with which a change in milk yield is associated with an increase or decrease in emissions intensity, we have to investigate the probability distributions (as shown in Fig. X) of emissions intensity at two levels of milk production. This can be achieved using the `varslice_resample` function for both production levels.

Let's look at this for production of 2000 and 3000 kg milk per capita per year. We'll take 1000 random draws of the emissions intensities that associated with both levels and compare values among these samples.

```{r}
slice_2000<-uncertainty::varslice_resample(in_var = dairy_households$y$pc_milk_yield,
                                 out_var = dairy_households$y$CO2eq_per_milk, 
                                 expectedin_var=2000,
                           n = 1000,
                           n_samples = 1000,
                           out_var_sampling = 1000)
slice_3000<-uncertainty::varslice_resample(in_var = dairy_households$y$pc_milk_yield,
                                 out_var = dairy_households$y$CO2eq_per_milk, 
                                 expectedin_var=3000,
                           n = 1000,
                           n_samples = 1000,
                           out_var_sampling = 1000)

sum(slice_3000$resampled < slice_2000$resampled) / length(slice_2000$resampled)

```
The comparison in the last line of code above reveals that in `r sum(slice_3000$resampled < slice_2000$resampled) / length(slice_2000$resampled)*100` % of cases, emissions intensity at the higher milk production level is lower than at the lower level.

We can now generalize this result by doing similar calculations for multiple production levels and illustrating them for the whole population.

in_var = dairy_households$y$pc_milk_yield
out_var = dairy_households$y$CO2eq_per_milk

milk_yields_to_sample<-seq(100,10000,100)
milk_yields_to_sample<-milk_yields_to_sample[which(milk_yields_to_sample<max(in_var))]
milk_yields_to_sample<-milk_yields_to_sample[which(milk_yields_to_sample>min(in_var))]
slices<-list()

# slice through the distribution at every 100 L milk yield per cow

for(i in 1:length(milk_yields_to_sample))
{slices[[i]]<-
  varslice_resample(in_var,
                      out_var,
                      expectedin_var = milk_yields_to_sample[i],
                      n_samples = 100000,
  out_var_sampling = 1000)$resample
 }

decreased_emissions_probability <-
  data.frame(Base_yield = NA,new_yield=NA,probability=NA)

for (i in 1:(length(milk_yields_to_sample) - 1))
{
  for (j in (i + 1):length(milk_yields_to_sample))
    {decreased_emissions_probability[nrow(decreased_emissions_probability)+1,"Base_yield"]<-milk_yields_to_sample[i]
     decreased_emissions_probability$new_yield[nrow(decreased_emissions_probability)]<-milk_yields_to_sample[j]
     decreased_emissions_probability$probability[nrow(decreased_emissions_probability)] <-
      sum(slices[[i]] > slices[[j]]) / length(slices[[i]])

}
}

decreased_emissions_probability<-decreased_emissions_probability[which(!is.na(decreased_emissions_probability$Base_yield)),]

decreased_emissions_probability[,"yield_increase"]<-decreased_emissions_probability$new_yield-decreased_emissions_probability$Base_yield

ggplot(data = decreased_emissions_probability, aes(Base_yield, yield_increase, z =
                                                      probability)) + geom_contour_filled() +
  ggtitle("Probability that emission intensity reductions occurred") + 
  xlab("Baseline milk yield per head and year (kg)") +
  ylab("Milk yield increase per head and year (kg)") +
  stat_contour(breaks = c(0.9),col="black")

ggsave("Fig_X1_probability_of_intensity_reduction.png")

The 90% confidence contour is shown in the plot. The results indicate that whenever milk yields increase, the probability that emissions intensity decreased is usually greater than 50% (slightly lower values are due to randomness in the resampling procedure), but that large increases are needed to be sure of this.

# Testing interventions - strategy

Farms may try to reduce their emissions intensity by making changes to their herd structure, feeding strategy or management practices. Programs aiming to effect emissions reductions in dairy production may want to reward such changes, and they may be looking to the milk production per capita as an indicator for the effectiveness of such measures. We now want explore whether this is a reasonable strategy.

## Strategy

Develop scenarios that implement innovations

* breed adjustment
* herd structure

Quantify improvements on farms by comparing with the baseline.
Plot improvements vs. the baseline on the above figure.
Plot improvements vs. baseline in the emissions intensity figure.

For each slice, and each level of confidence, calculate the percentage of farms that made changes that would be correctly rewarded vs. the ones that did not change (the baseline population). Make a figure showing the Type I and Type II errors resulting from each confidence level at each baseline yield.

# Testing interventions

## Single-run function

To clearly characterize the impact of interventions, we should compare their impact with a counterfactual, i.e. with the same farms without the intervention. While this is usually impossible in practice, it is easy with a model. We just have to run the simulation again with identical inputs except for those that are affected by the intervention.

We already simulated emissions for a large population of farms, and we can now apply our interventions to this population by modifying certain parameters of the input tables. What we don't want now, however, is to randomize all values again, since this would add additional noise to the results, which would mask the signal caused by the interventions.

We now first need a function that can apply our greenhouse gas emissions model to a pre-defined set of input values. We can find syntax that can achieve this in the mcSimulation function. Here it is (with slight modifications):

```{r}
run_model<-function(x_data,model)
  {
  varnames<-colnames(x_data)[which(!colnames(x_data)=="Scenario")]
  model_function_ <- function(x) {

    e <- as.list(sapply(X = varnames, FUN = function(i) as.numeric(unlist(x[i]))))
    eval(expr = body(model), envir = e)
  }
  y <- do.call(what = rbind, args = lapply(X = apply(X = x_data, 
                                                     MARGIN = 1, FUN = model_function_), FUN = unlist))
  returnObject <- list(y = data.frame(y), x = data.frame(x_data))
  returnObject$call <- match.call()
  class(returnObject) <- cbind("mcSimulation", class(returnObject))
  return(returnObject)
}

The following code can precisely reproduce the results of the previous analysis:

```{r, eval=FALSE}
res<-run_model(GHG_simulation_scenarios$x,ghg_emissions)
```

To simulate interventions, we can now feed this function with modified x_data data.frames.

## Breed intervention

Introduction of higher-performance breeds may reduce greenhouse gas emissions. We simulate an intervention that replaces animals of low-performance breeds with animals of high-performance breeds.

To retain the farm-specific performance levels obtained from the farm survey, we simulate these impacts in a relative manner. For this, we first need to determine the performance and characteristics of each of the breeds. We'll base this on the farm survey data (`Kenyaherds` dataset from above).

```{r}
cows<-Kenyaherds[which(Kenyaherds$animal_type %in% 4:6),]

ggplot(cows, aes(factor(breed),milk_yield)) +
  geom_violin(draw_quantiles=c(0.5),fill="light green") +
  xlab("Breed") + ylab("Milk yield (kg per day)") + theme_bw()

milk_summary<-cbind(aggregate(cows$milk_yield, by=list(cows$breed), FUN=median),table(cows$breed))
milk_summary<-milk_summary[,c(1,4,2)]
colnames(milk_summary)<-c("Breed","n","Median_milk_yield")
milk_summary

This evaluation shows that the difference in median milk yields is relatively small, but that the milk yield distributions show a lot of variation that is apparently not explained by the breed. It is also apparent that the number of animals these estimates are based on varies considerably. Two breeds make up `r round(sum(milk_summary$n[1:2])/sum(milk_summary$n)*100,1)` % of the entire population, with others having very few animals, which means that the medians may be somewhat unreliable (especially for the single animal of breed 7).

Let's define the intervention as follows:

All animals are replaced by high-performance animals of breed 1, which increases milk yields proportionally to the median milk yield differences. This means that milk yields are multiplied by the following factors:

```{r}
milk_summary[,"Intervention_factor"]<-sapply(milk_summary$Median_milk_yield, function(x) min(x/milk_summary$Median_milk_yield[1],1))

milk_summary             
```

A change of the breed also causes changes in weight, mature weight and weight gain.

```{r}
live_weights<-aggregate(Kenyaherds$live_weight_LW, by=list(Kenyaherds$animal_type,Kenyaherds$breed), FUN=median)
colnames(live_weights)<-c("animal_type","breed","median_live_weight")
live_weights[,"Intervention_factor"]<-NA
for(i in 1:nrow(live_weights))
  live_weights$Intervention_factor[i]<-live_weights$median_live_weight[i]/
     live_weights$median_live_weight[which(live_weights$animal_type==live_weights$animal_type[i] &                                                                                                            live_weights$breed==1)]

# mature weight should probably be changed, and the code below does this. However, the mature weight is currently the same for all the breeds, so this accomplished nothing.

mature_weights<-aggregate(Kenyaherds$mature_weight_MW, by=list(Kenyaherds$animal_type,Kenyaherds$breed), FUN=median)
colnames(mature_weights)<-c("animal_type","breed","median_mature_weight")
mature_weights[,"Intervention_factor"]<-NA
for(i in 1:nrow(mature_weights))
  mature_weights$Intervention_factor[i]<-mature_weights$median_mature_weight[i]/
     mature_weights$median_mature_weight[which(mature_weights$animal_type==mature_weights$animal_type[i] &                                                                                                            mature_weights$breed==1)]

# same for the weight gain - doesn't depend on the breed at the moment, so all the factors are 1

weight_gains<-aggregate(Kenyaherds$weight_gain_WG, by=list(Kenyaherds$animal_type,Kenyaherds$breed), FUN=median)
colnames(weight_gains)<-c("animal_type","breed","median_weight_gain")
weight_gains[,"Intervention_factor"]<-NA
for(i in 1:nrow(weight_gains))
  weight_gains$Intervention_factor[i]<-weight_gains$median_weight_gain[i]/
     weight_gains$median_weight_gain[which(weight_gains$animal_type==weight_gains$animal_type[i] &                                                                                                            weight_gains$breed==1)]
weight_gains$Intervention_factor[which(weight_gains$median_weight_gain==0)]<-1

Now we can modify the input table accordingly.

go through all the farms. Determine the 'improvement' coefficients (based on herd structure)

```{r}
farms<-unique(Kenyaherds$QQNO)
breed_intervention<-data.frame(Farm=farms, milk_yield_4=1, milk_yield_5=1, milk_yield_6=1)

Kenyaherds_interventions<-Kenyaherds[,c("QQNO",
                                        "system",
                                        "animal_type",
                                        "breed",
                                        "live_weight_LW",
                                        "mature_weight_MW",
                                        "weight_gain_WG",
                                        "milk_yield",
                                        "dig_energy",
                                        "CP.")]

Kenyaherds_interventions[,"milk_change"]<-0
cows<-which(Kenyaherds_interventions$animal_type %in% 4:6)
Kenyaherds_interventions$milk_change[cows]<- sapply(cows,function(x) 1/milk_summary$Intervention_factor[milk_summary$Breed==Kenyaherds_interventions$breed[x]]  )

milk_change<-aggregate(Kenyaherds_interventions$milk_change[cows], by=list(Kenyaherds_interventions$QQNO[cows]), FUN=mean)

breed_intervention$milk_yield_4[which(breed_intervention$Farm %in% milk_change[,1])]<-milk_change[,2]
breed_intervention$milk_yield_5<-breed_intervention$milk_yield_4
breed_intervention$milk_yield_6<-breed_intervention$milk_yield_4

for(i in 1:nrow(Kenyaherds_interventions))
  {Kenyaherds_interventions[i,"live_weight_change"]<-
    1/live_weights$Intervention_factor[which(live_weights$animal_type==Kenyaherds_interventions$animal_type[i]&
                                             live_weights$breed==Kenyaherds_interventions$breed[i])]
#   Kenyaherds_interventions[i,"mature_weight_change"]<-
#      1/mature_weights$Intervention_factor[which(mature_weights$animal_type==Kenyaherds_interventions$animal_type[i]&
#                                                 mature_weights$breed==Kenyaherds_interventions$breed[i])]
   Kenyaherds_interventions[i,"weight_gain_change"]<-
     1/weight_gains$Intervention_factor[which(weight_gains$animal_type==Kenyaherds_interventions$animal_type[i]&
                                              weight_gains$breed==Kenyaherds_interventions$breed[i])]
}

live_weight_agg<-aggregate(Kenyaherds_interventions$live_weight_change,
                           by=list(Kenyaherds_interventions$QQNO,Kenyaherds_interventions$animal_type), FUN=mean)
#mature_weight_agg<-aggregate(Kenyaherds_interventions$mature_weight_change,
#by=list(Kenyaherds_interventions$QQNO,Kenyaherds_interventions$animal_type), FUN=mean)
weight_gain_agg<-aggregate(Kenyaherds_interventions$weight_gain_change,
                           by=list(Kenyaherds_interventions$QQNO,Kenyaherds_interventions$animal_type), FUN=mean)

colnames(live_weight_agg)<-c("farm","animal_type","conv_factor")
#colnames(mature_weight_agg)<-c("farm","animal_type","conv_factor")
colnames(weight_gain_agg)<-c("farm","animal_type","conv_factor")

for(i in 1:nrow(live_weight_agg))
  breed_intervention[which(breed_intervention$Farm==live_weight_agg$farm[i]),
                     paste0("live_weight_LW_",live_weight_agg$animal_type[i])]<-
    live_weight_agg$conv_factor[i]

#for(i in 1:nrow(mature_weight_agg))
#  breed_intervention[which(breed_intervention$Farm==mature_weight_agg$farm[i]),
#                     paste0("mature_weight_LW_",mature_weight_agg$animal_type[i])]<-
#    mature_weight_agg$conv_factor[i]

for(i in 1:nrow(weight_gain_agg))
  breed_intervention[which(breed_intervention$Farm==weight_gain_agg$farm[i]),
                     paste0("weight_gain_WG_",weight_gain_agg$animal_type[i])]<-
    weight_gain_agg$conv_factor[i]

breed_intervention[is.na(breed_intervention)]<-1

go through the x file
for each row take a random draw based on adoption rate (does farm adopt or not), then (possibly) apply factors. Actually, in this case we want to simulate full adoption, so we'll set this to 1.

```{r, eval=FALSE}
x_breed_intervention <- GHG_simulation_scenarios$x

adoption_rate <- 1

for (i in 1:nrow(x_breed_intervention))
{
  if (rbinom(1, 1, adoption_rate)) # if farmers adopt, make changes in x file
    x_breed_intervention[i, colnames(breed_intervention)[2:ncol(breed_intervention)]] <-
      x_breed_intervention[i, colnames(breed_intervention)[2:ncol(breed_intervention)]] *
      breed_intervention[which(paste0("Farm_", breed_intervention$Farm) ==
                                 x_breed_intervention$Scenario[i]),
                         2:ncol(breed_intervention)]
}
# run model for modified x file
breed_res <- run_model(x_breed_intervention, ghg_emissions)

```{r, include=FALSE, eval=FALSE}
breed_res$call<-"multi-scenario call"
save_temperature_scenarios(breed_res,"results","Breed_intervention")
```

```{r, include=FALSE}
adoption_rate <- 1
breed_res<-load_temperature_scenarios("results","Breed_intervention")
class(breed_res)<-"mcSimulation"
```

# Compare outcomes of breed intervention with baseline

```{r}
breed_res$y[,"CO2eq_per_milk"]<-breed_res$y$pc_on_farm/breed_res$y$pc_milk_yield

breed_res$y<-breed_res$y[which(GHG_simulation_scenarios$y$pc_milk_yield>500),]
breed_res$x<-breed_res$x[which(GHG_simulation_scenarios$y$pc_milk_yield>500),]

impact_of_breed<-data.frame(baseline=dairy_households$y$pc_milk_yield,breed_milk=breed_res$y$pc_milk_yield,CO2_intensity_baseline= dairy_households$y$CO2eq_per_milk,CO2_intensity_breed=breed_res$y$CO2eq_per_milk)
impact_of_breed[,"milk_change"]<-round(impact_of_breed$breed_milk-impact_of_breed$baseline,2)
impact_of_breed[,"emissions_intensity_change"]<-round(impact_of_breed$CO2_intensity_breed-impact_of_breed$CO2_intensity_baseline ,3)

ggplot(data=impact_of_breed,aes(x=milk_change,y=emissions_intensity_change)) + geom_point() + theme_bw() + ylab("Change in emissions intensity (kg CO2-eq kg-1)") + xlab("Change in per capita milk yield (kg)")

ggsave("Fig_XX_breed_reductions.png")

ggplot(data = decreased_emissions_probability, aes(Base_yield, yield_increase)) + geom_contour_filled(aes(z=probability)) +
  stat_contour(breaks = c(0.9),aes(z=probability),col="black") +
  geom_point(data=impact_of_breed[which(impact_of_breed$milk_change>0),],aes(x=baseline,y=milk_change)) +
  ggtitle("Probability that emission intensity reductions occurred") + 
  xlab("Baseline milk yield per head and year (kg)") +
  ylab("Milk yield increase per head and year (kg)") 
ggsave("Fig_XX1_breed_probability_of_intensity_reduction.png")

This plot shows a lot of linear patterns that result from the application of fixed factors to convert the milk yield between cows of different breeds. Not so pretty, but maybe ok.

## Herd structure

### Retiring unproductive bulls

To simulate this scenario, we simply have to remove all animals of type 1 from the herds.

```{r , warning=FALSE, eval=FALSE}
x_nobull_intervention <- GHG_simulation_scenarios$x

nobull_adoption_rate <- 1.0

for (i in 1:nrow(x_nobull_intervention))
{
  if (rbinom(1, 1, nobull_adoption_rate)) # if farmers adopt, make changes in x file
    x_nobull_intervention$N_animal_type_1[i]<-0
}
# run model for modified x file
nobull_res <- run_model(x_nobull_intervention, ghg_emissions)

```{r, include=FALSE, eval=FALSE}
nobull_res$call<-"multi-scenario call"
save_temperature_scenarios(nobull_res,"results","noBull_intervention")
```

```{r, include=FALSE}
nobull_res<-load_temperature_scenarios("results","noBull_intervention")
class(nobull_res)<-"mcSimulation"
```

#### Evaluate impact of "Retiring unproductive bulls" intervention

We're assuming that all bulls >36 months old have been removed.

```{r, fig.show="hold", out.width="50%", fig.cap="No bulls intervention (left) vs. baseline (right)", message=FALSE}

uncertainty::varscatter(in_var = nobull_res$y$pc_milk_yield,
                        out_var = nobull_res$y$pc_on_farm,
                        xlab = expression(Total~milk~yield~(kg~head^{-1}~year^{-1})),
                        ylab = expression(Total~emissions~(kg~CO[2]-eq~head^{-1}~year^{-1})))

uncertainty::varscatter(in_var = GHG_simulation_scenarios$y$pc_milk_yield,
                        out_var = GHG_simulation_scenarios$y$pc_on_farm,
                        xlab = expression(Total~milk~yield~(kg~head^{-1}~year^{-1})),
                        ylab = expression(Total~emissions~(kg~CO[2]-eq~head^{-1}~year^{-1})))

uncertainty::varkernel(in_var = nobull_res$y$pc_milk_yield,
                        out_var = nobull_res$y$pc_on_farm,
                        xlab = expression(Total~milk~yield~(kg~head^{-1}~year^{-1})),
                        ylab = expression(Total~emissions~(kg~CO[2]-eq~head^{-1}~year^{-1})))

uncertainty::varkernel(in_var = GHG_simulation_scenarios$y$pc_milk_yield,
                        out_var = GHG_simulation_scenarios$y$pc_on_farm,
                        xlab = expression(Total~milk~yield~(kg~head^{-1}~year^{-1})),
                        ylab = expression(Total~emissions~(kg~CO[2]-eq~head^{-1}~year^{-1})))

### Reducing unproductive replacement males

The idea is to raise the off-take rate of replacement males by 23% (not sure why this number). We'll implement this by eliminating replacement males on all adopting farms, with a 23% adoption rate. The result should be quite similar.

```{r , warning=FALSE, eval=FALSE}
x_lessReplace_intervention <- GHG_simulation_scenarios$x

lessReplace_adoption_rate <- 0.23

for (i in 1:nrow(x_lessReplace_intervention))
{
  if (rbinom(1, 1, lessReplace_adoption_rate)) # if farmers adopt, make changes in x file
    x_lessReplace_intervention$N_animal_type_3[i]<-0
}
# run model for modified x file
lessReplace_res <- run_model(x_lessReplace_intervention, ghg_emissions)

```{r, include=FALSE, eval=FALSE}
lessReplace_res$call<-"multi-scenario call"
save_temperature_scenarios(lessReplace_res,"results","lessReplace_intervention")
```

```{r, include=FALSE}
lessReplace_res<-load_temperature_scenarios("results","lessReplace_intervention")
class(lessReplace_res)<-"mcSimulation"
```

# Compare outcomes of herd intervention with baseline

## No bulls scenario

```{r}
nobull_res$y[,"CO2eq_per_milk"]<-nobull_res$y$pc_on_farm/nobull_res$y$pc_milk_yield

nobull_res$y<-nobull_res$y[which(GHG_simulation_scenarios$y$pc_milk_yield>500),]
nobull_res$x<-nobull_res$x[which(GHG_simulation_scenarios$y$pc_milk_yield>500),]

impact_of_nobull<-data.frame(baseline=dairy_households$y$pc_milk_yield,breed_milk=nobull_res$y$pc_milk_yield,CO2_intensity_baseline= dairy_households$y$CO2eq_per_milk,CO2_intensity_breed=nobull_res$y$CO2eq_per_milk)
impact_of_nobull[,"milk_change"]<-round(impact_of_nobull$breed_milk-impact_of_nobull$baseline,2)
impact_of_nobull[,"emissions_intensity_change"]<-round(impact_of_nobull$CO2_intensity_breed-impact_of_nobull$CO2_intensity_baseline ,3)

ggplot(data=impact_of_nobull,aes(x=milk_change,y=emissions_intensity_change)) + geom_point() + theme_bw() + ylab("Change in emissions intensity (kg CO2-eq kg-1)") + xlab("Change in per capita milk yield (kg)")

ggplot(data = decreased_emissions_probability, aes(Base_yield, yield_increase)) + geom_contour_filled(aes(z=probability)) +
  stat_contour(breaks = c(0.9),aes(z=probability),col="black") +
  geom_point(data=impact_of_nobull[which(impact_of_nobull$milk_change>0),],aes(x=baseline,y=milk_change)) +
  ggtitle("Probability that emission intensity reductions occurred") + 
  xlab("Baseline milk yield per head and year (kg)") +
  ylab("Milk yield increase per head and year (kg)") 
ggsave("Fig_XX1_breed_probability_of_intensity_reduction.png")

ggsave("Fig_XX_impact_of_nobull_reductions.png")

## Fewer replacement males scenario

lessReplace_res$y[,"CO2eq_per_milk"]<-lessReplace_res$y$pc_on_farm/lessReplace_res$y$pc_milk_yield

lessReplace_res$y<-lessReplace_res$y[which(GHG_simulation_scenarios$y$pc_milk_yield>500),]
lessReplace_res$x<-lessReplace_res$x[which(GHG_simulation_scenarios$y$pc_milk_yield>500),]

impact_of_lessReplace<-data.frame(baseline=dairy_households$y$pc_milk_yield,breed_milk=lessReplace_res$y$pc_milk_yield,CO2_intensity_baseline= dairy_households$y$CO2eq_per_milk,CO2_intensity_breed=lessReplace_res$y$CO2eq_per_milk)
impact_of_lessReplace[,"milk_change"]<-round(impact_of_lessReplace$breed_milk-impact_of_lessReplace$baseline,2)
impact_of_lessReplace[,"emissions_intensity_change"]<-round(impact_of_lessReplace$CO2_intensity_breed-impact_of_lessReplace$CO2_intensity_baseline ,3)

ggplot(data=impact_of_lessReplace,aes(x=milk_change,y=emissions_intensity_change)) + geom_point() + theme_bw() + ylab("Change in emissions intensity (kg CO2-eq kg-1)") + xlab("Change in per capita milk yield (kg)")

ggplot(data = decreased_emissions_probability, aes(Base_yield, yield_increase)) + geom_contour_filled(aes(z=probability)) +
  stat_contour(breaks = c(0.9),aes(z=probability),col="black") +
  geom_point(data=impact_of_lessReplace[which(impact_of_lessReplace$milk_change>0),],aes(x=baseline,y=milk_change)) +
  ggtitle("Probability that emission intensity reductions occurred") + 
  xlab("Baseline milk yield per head and year (kg)") +
  ylab("Milk yield increase per head and year (kg)") 
ggsave("Fig_XX1_breed_probability_of_intensity_reduction.png")

ggsave("Fig_XX_lessReplace_reductions.png")
